Stat 400 Project

### 2021-12-07 Stat 400 proj.Rmd
Got a bootstrap confidence interval graph

  #Create data frame to store confidence intervals
  ci_df <- matrix(data=NA, nrow=days + 1, ncol=2)
  ci_df <- data.frame(ci_df)

@@

  for(i in 1:ncol(samps)){
    #Make sure column has more than one unique value
    check <- (length(unique(samps[ ,i])) != 1)
    if(check){
    boot_obj <- boot(samps[ ,i], mean_func, 2000)
    ci_obj <- boot.ci(boot_obj, conf = .95, type = ci_type)
    ci_df[i, ] <- c(ci_obj$percent[4], ci_obj$percent[5])
    }else{ci_df[i, ] <- c(samps[1, i], samps[1, i])}
  }
return(ci_df)
}

get_bootstrap_cis(days=50, num_subjects=100, x_dim=10, y_dim=10, I_0=2, inf_dist=1, sample_size=5)

>>>>

  #Create data frame to store confidence intervals
  ci_df <- matrix(data=NA, nrow=days + 1, ncol=3)
  ci_df <- data.frame(ci_df)

@@

  for(i in 1:ncol(samps)){
    #Make sure column has more than one unique value
    check <- (length(unique(samps[ ,i])) != 1)
    if(check){
    boot_obj <- boot(samps[ ,i], mean_func, 2000)
    ci_obj <- boot.ci(boot_obj, conf = .95, type = ci_type)
    ci_df[i, 1] <- ci_obj$percent[4]
    ci_df[i, 2] <- ci_obj$t0
    ci_df[i, 3] <- ci_obj$percent[5]
    }else{ci_df[i, ] <- c(samps[1, i], samps[1, i], samps[1, i])}
  }
return(ci_df)
}

plot_dat <- get_bootstrap_cis(days=50, num_subjects=100, x_dim=10, y_dim=10, I_0=2, inf_dist=1, sample_size=5)

ggplot() +
  geom_line(aes(x=1:51, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:51, y=plot_dat[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat[ ,3]), linetype = 2, color = 'red')
